Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2024-10-20 paper.tex
Fix typos

The first set of simulations is performed for the long-wave steepness of
$\varepsilon_L = 0.1$, $0.2$, and $0.4$ (Fig. \ref{fig:numerical_solutions}).
The long-waves are initialised from rest ($a_L = 0$) and gradually ramped up
to their target steepness over 5 long-wave periods, thus emulating the passage
of a long-wave group
(the importance of which we discuss in more detail in the next subsection).
At $\varepsilon = 0.1$, the numerical solutions for the wavenumber, amplitude,
and steepness modulation are all remarkably similar to the analytical solutions
(Fig. \ref{fig:numerical_solutions}a,d,g).
This suggests that at low long-wave steepness that the steady analytical solution
is a reasonable proxy for the fully-nonlinear crest-action conservation
equation solutions.
The numerical solutions diverge more notably from the analytical ones at
moderate steepness of 0.2 (Fig. \ref{fig:numerical_solutions}b,e,h), and are
considerably different at very high steepness of 0.4
(Fig. \ref{fig:numerical_solutions}c,f,i).
These differences suggest that at high steepness the inhomogeneity of
gravitational acceleration and group speed, otherwise ignored in the steady
solutions, become important.

@@

We now proceed to examine the numerical solutions with the long-wave forcing
applied as a long-wave group.
The wave group is simulated as a non-dispersive train of long waves whose
amplitude scales with $\sin[\pi t / (n T_L)]$, where $n$ is the number of
long waves in the group.
The elevation of the long waves thus gradually ramps up from rest to $a_L$ at
$t = n T_L / 2$, after which it gradually decreases toward zero.
In this simulation, $n = 10$ and $\varepsilon_L = 0.1$ as in the previous two
simulations.
The modulations of short-wave wavenumber, amplitude, and steepness in response
to such long-wave group is shown in Fig. \ref{fig:modulation_3panel_groups}.
Like in the case of a linear ramp, the modulation pattern here is locked in to
the long-wave crest and peaks at approximately 1.2 for short-wave steepness.
After the peak of the long-wave group passes, the short-wave modulation recedes
back toward the resting state.

>>>>

The first set of simulations is performed for the long-wave steepness of
$\varepsilon_L = 0.1$, $0.2$, and $0.4$ (Fig. \ref{fig:numerical_solutions}).
The long-waves are initialised from rest ($a_L = 0$) and gradually ramped up
to their target steepness over 5 long-wave periods, thus emulating the passage
of a long-wave group
(the importance of which we discuss in more detail in the next subsection).
At $\varepsilon_L = 0.1$, the numerical solutions for the wavenumber, amplitude,
and steepness modulation are all remarkably similar to the analytical solutions
(Fig. \ref{fig:numerical_solutions}a,d,g).
This suggests that for low long-wave steepness the steady analytical solution
is a reasonable proxy for the fully-nonlinear crest-action conservation
equation solutions.
The numerical solutions diverge more notably from the analytical ones at
moderate steepness of 0.2 (Fig. \ref{fig:numerical_solutions}b,e,h), and are
considerably different at very high steepness of 0.4
(Fig. \ref{fig:numerical_solutions}c,f,i).
These differences suggest that at high steepness the inhomogeneity of
gravitational acceleration and group speed, otherwise ignored in the steady
solutions, become important.

@@

We now proceed to examine the numerical solutions with the long-wave forcing
applied as a long-wave group.
The wave group is simulated as a non-dispersive train of long waves whose
amplitude scales with $\sin[\pi t / (n T_L)]$, where $n$ is the number of
long waves in the group.
The elevation of the long waves thus gradually ramps up from rest to $a_L$ at
$t = n T_L / 2$, after which it gradually decreases toward zero.
In this simulation, $n = 10$ and $\varepsilon_L = 0.1$ as in the previous two
simulations.
The modulations of short-wave wavenumber, amplitude, and steepness in response
to such long-wave group is shown in Fig. \ref{fig:modulation_3panel_groups}.
Like in the case of a linear ramp, the modulation pattern here is locked in to
the long-wave crest and peaks at approximately 1.2 for short-wave steepness of 0.1.
After the peak of the long-wave group passes, the short-wave modulation recedes
back toward the resting state.
